\documentclass[10pt, conference, compsocconf]{IEEEtran}
%IEEEtran
%acmart

\usepackage{flushend}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{array}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{color}
\usepackage{pdfpages}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
	language=Java,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}


\begin{document}
\title{Predicting Co-Changes between Functionality Specifications and Source Code in Behavior Driven Development}

\author{\IEEEauthorblockN{Aidan Z.H. Yang}
	\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
		\textit{Queen's University}\\
		Kingston, Ontario, Canada \\
		a.yang@queensu.ca}
	\and
	\IEEEauthorblockN{Daniel Alencar da Costa}
	\IEEEauthorblockA{\textit{Department of Information Science} \\
		\textit{University of Otago}\\
		Dunedin, Otago, New Zealand \\
		danielcalencar@otago.ac.nz}
	\and
	\IEEEauthorblockN{Ying Zou}
	\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
		\textit{Queen’s University}\\
		Kingston, Ontario, Canada \\
		ying.zou@queensu.ca}
	}

\maketitle

\begin{abstract}
Behavior Driven Development (BDD) is an agile approach that uses \textit{.feature} files to describe the functionalities of a software system using natural language constructs (English-like phrases). Because of the English-like structure of \textit{.feature} files, BDD specifications become an evolving documentation that helps all (even non-technical) stakeholders to understand and contribute to a software project. After specifying a \textit{.feature} files, developers can use a BDD tool (e.g., Cucumber) to automatically generate test cases and implement the code of the specified functionality. However, maintaining traceability between \textit{.feature} files and source code requires human efforts. Therefore, \textit{.feature} files can be out-of-date, reducing the advantages of using BDD. Furthermore, existing research do not attempt to improve the traceability between \textit{.feature} files and source code files. In this paper, we study the co-changes between \textit{.feature} files and source code files to improve the traceability between \textit{.feature} files and source code files. Due to the English-like syntax of \textit{.feature} files, we use natural language processing to identify co-changes, with an accuracy of 79\%. We study the characteristics of BDD co-changes and build random forest models to predict when a \textit{.feature} files should be modified before committing a code change. The random forest model obtains an AUC of 0.77. The model can assist developers in identifying when a \textit{.feature} files should be modified in code commits. Once the traceability is up-to-date, BDD developers can write test code more efficiently and keep the software documentation up-to-date. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%

\begin{IEEEkeywords}Behavior Driven Development, Traceability, Co-Changes, Empirical Software Engineering
\end{IEEEkeywords}


\input{introduction}
\input{example}
\input{experiment_setup}
\input{RQ1}
\input{RQ2}
\input{RQ3}
\input{threats}
\input{related_works}
\input{conclusion}


\bibliographystyle{ieeetran}
%ieeetran
%apacite
\bibliography{references}


\end{document}
